% !TEX root = ../thesis.tex

This thesis is the result of 10 months of work between December 2016 and September 2017, for the degree of Master of Science in Engineering, in the Physics Department of KTH Royal Institute of Technology, Sweden.

\section*{Acknowledgements}

I would like to thank my supervisor Prof.\ Egor Babaev for giving me the opportunity to carry out my degree project in the Statistical Physics group. Your encouragement and support have been greatly appreciated, as well as your patience for results from my, sometimes extremely bug prone, code. I would also like to extend my deepest gratitude to Johan Carlström who, as an expert in the field, has provided excellent guidance throughout the project. Furthermore I would like to thank Prof.\ Nikolay Prokof'ev from University of Massachusetts Amherst for helping me sort out problems no one else was able to. Last but not least I would like to express my gratitude towards my fellow master degree students as well as to my soon-to-be fellow Ph.D students at the Physics Department for helping me with various issues.

\section*{Units}

Throughout this text $ k_\text{B} = \hbar = 1 $ has been used. With this notation there is no difference between wave vectors and momentum, which is the reason why they are sometimes used interchangeably.

\section*{Definitions}

At a few instances the symbol $ \dotDelta $ appears. This is an invented shorthand notation defined as $ \dotDelta x \equiv \Delta x / 2 $ used to make certain expressions appear less cluttered. 